% ==========================================
% SECTION 1: INTRODUCTION (20%)
% ==========================================
\section{Introduction}

\subsection{Project Summary (5\%)}
% Present a clear summary of the project to contextualise its main motivation and goals.

\subsubsection{Project Context}
At Durham University, the Strategic Planning and Insight Office (SPIO) ensure Durham's course offerings remain attractive to prospective students by monitoring competitor programmes. Analysis of competitor data, including pricing and program structure, helps position courses to meet prospective student demand. 

\subsubsection{Problem Statement}
The department relies on a commercial third-party dataset for higher education competitor data. Whilst better than collecting manually, several limitations are introduced. Only one dataset is provided each year, meaning the department is reliant on static data within a changing field. The scope and structure of the data regarding universities, programmes and course options is fixed, providing little flexibility or control over detail. As a result, market research is limited, and responding to market changes is difficult. 

\subsubsection{Project Objective}
To overcome these constraints, the project proposes a bespoke automated competitor data collection and analysis system. Controlling the data collection pipeline provides control over the frequency, scope, structure, and granularity of the data. The platform will support comparisons across institutions, also providing the capability to export filtered datasets for further analysis, in addition to an insight dashboard for graphical visualisations. While the current implementation prioritises data processing and core analytical tools for the users, advanced predictive modelling and integration with internal university systems falls outside the scope due to the aims and scale set by the stakeholder. 
The success of the solution will be evaluated against a set of project objectives defined later through metrics representative of the stakeholder aims, linked to the system features and behavioural requirements.

\subsubsection{Proposed Solution}
To meet these objectives, the proposed system will collect, process and present competitor courses from UCAS and a selection of institution websites, made available through a web-based application. Data cleansing and normalisation will provide consistent, structured formatting across the different sources. The web-based UI will fetch from a local PostgreSQL relational database for efficient querying and filtering of the competitor data. Additional capabilities, such as scraping process management, searching, filtering, exporting and visualisation will also be available to the SPIO users.  


\subsection{System Access and Setup (5\%)}
% Provide usable access to the developed system (URL if online, or zip instructions).
% Clear instructions on how to set it up and run it.

\subsubsection{Source Code Repository}
The complete source code for this project is available through this public repository:

\begin{commandbox}
https://github.com/COMP2281/software-engineering-group25-26-19
\end{commandbox}

\subsubsection{System Requirements}
The system requires the following third-party components: Node.js (v18+), PostgreSQL database, npm package manager, Git and a web browser. 

\subsubsection{Basic Installation Steps}
Clone the repository:

\begin{commandbox}
    git clone https://github.com/COMP2281/software-engineering-group25-26-19.git
\end{commandbox}
Install dependencies (in frontend and backend):
\begin{commandbox}
    npm install
\end{commandbox}
Start application services:
\begin{commandbox}[/backend]
    npm run build \\
    npm run start
\end{commandbox}

\subsection{Behavioural Requirements Status (10\%)}
% Requirement: Table with Code, Description, Status (Unchanged/Modified), Met/Not Met.

\subsubsection{Overview of System Behaviour}

The behavioural requirements set out in the requirements documentation describe the functionality available to the SPIO users to support their required analysis. The system focuses on allowing users to collect, explore and analyse competitor programme information through a set of core features. These features ensure stakeholders can carry out the required operations identified during the requirements phase. 

Although historical data was not provided by the stakeholder, the system is designed to accumulate data in future scrapes, allowing historical trends to be viewed as the datasets grow. 

\subsubsection{Implemented Behavioural Features}
\vspace{-8pt}
\setlength{\tabcolsep}{6pt}
\begin{xltabular}{\textwidth}{@{} l p{1.5cm} p{2.5cm} p{3.5cm} X @{}}
\caption{Status of Behavioural Requirements} \\
\toprule
\textbf{Code} & \textbf{Feature} &\textbf{Description} & \textbf{Change} & \textbf{Met/Justification} \\
\midrule
\endfirsthead
\toprule
\textbf{Code} & \textbf{Feature} &\textbf{Description} & \textbf{Change} & \textbf{Met/Justification} \\
\midrule
\endhead
\bottomrule
\endlastfoot

BR 1.1 & Login & Successful login with valid credentials & \textbf{Unchanged} & \textbf{Met --} Valid users are authenticated and redirected to the requested protected route, defaults to dashboard. \\
BR 1.2 & Login & Failed login with incorrect password & \textbf{Unchanged} & \textbf{Met --} Incorrect credentials trigger an authentication error message and prevent access to protected routes. \\
BR 1.3 & Login & Unauthenticated access attempt & \textbf{Unchanged} & \textbf{Met --} Unauthenticated access redirects user to login page with an error message. \\

\midrule

BR 2.1 & Fetch Data & Successful initiation of fetch & \textbf{Unchanged} & \textbf{Met --} Fetch initiated from dashboard or courses page, with optional filtering. \\

BR 2.2 & Fetch Data & Fetch whilst in progress & \textbf{Unchanged} & \textbf{Met --} If fetch in progress, additional requests are blocked with error message. \\

\midrule

BR 3.1 & Export Data & Successful export to excel & \textbf{Modified --} Export from dashboard (all) or courses (specific). & \textbf{Met --} Excel file generated containing specified dataset and download initiated. \\

BR 3.2 & Export Data & Exporting empty dataset & \textbf{Modified --} On courses page, export disabled when no data is available. & \textbf{Met --} When no data available, export either returns an error (dashboard page), or export functionality is unavailable (courses page). \\

\midrule

BR 4.1 & Visualisa-tion & Visualised fetched data & \textbf{Unchanged} & \textbf{Met --} Visualisation page supports graphical trend analysis with multi-year data. \\
BR 4.2 & Visualisa-tion & Update graphs after new data & \textbf{Unchanged} & \textbf{Met --} Graphs update when new data collected, trends improve as data builds. \\
BR 4.3 & Visualisa-tion & Graph view manipulation & \textbf{Unchanged} & \textbf{Met --} Interactive tools to change the presented dataset within a specific graph. \\

\midrule

BR 5.1 & Search Data & Matching results & \textbf{Unchanged} & \textbf{Met --} Courses whose title or description matches the specified term are returned. \\
BR 5.2 & Search Data & Returns partial matches & \textbf{Unchanged} & \textbf{Met --} Search returns courses matching the keyword as a substring. \\
BR 5.3 & Search Data & Search returns no results & \textbf{Unchanged} & \textbf{Met --} If no courses match, table remains empty and a message is displayed. \\

\midrule

BR 6.1 & Filter Data & Filter by Institution & \textbf{Modified --} Select multiple institutions. & \textbf{Met --} Can select one or more institutions, returning courses from all. \\
BR 6.2 & Filter Data & Combined filters & \textbf{Unchanged} & \textbf{Met --} Multiple filters can be combined, message shown if no results for all criteria. \\

\midrule

BR 7.1 & Historical Data & Tuition fee history & \textbf{Unchanged} & \textbf{Met --} Tuition fee trend graphs for each available course option on details page. \\

BR 7.2 & Historical Data & Course comparison & \textbf{Unchanged} & \textbf{Met --} Presents all available years for comparison of course options. \\

\midrule

BR 8.1 & Dashboard Overview & Display key information & \textbf{Unchanged} & \textbf{Met --} Displays key metrics, including total courses and last updated. \\
BR 8.2 & Dashboard Overview & Quick Fetch & \textbf{Unchanged} & \textbf{Met --} 'Start Scraper' initiates default data collection, with status displayed. \\
BR 8.3 & Dashboard Overview & Quick Export & \textbf{Unchanged} &\textbf{Met --} Export button generates an Excel file of dataset and initiates download. \\

\midrule

BR 9.1 & Compari-son & Add courses for comparison & \textbf{Modified --} Comparison bar removed. & \textbf{Met --} Courses across multiple pages can be selected for comparison. \\
BR 9.2 & Compari-son & View course comparison & \textbf{Modified --} Selectable on comparison page. & \textbf{Met --} Comparison page shows selected courses options side-by-side, with key attributes such as tuition fees. \\

\midrule

BR 10.1 & Fee Prediction & Predict Fee & \textbf{Unchanged} & \textbf{Not Met --} Identified as a 'Won't Have', a predictive algorithm needs historical data. \\
BR 10.2 & Fee Prediction & Insufficient History & \textbf{Unchanged} & \textbf{Not Met --} Dependent on predictive modelling feature, which was not implemented. \\
BR 10.3 & Fee Prediction & Historical Visualisation & \textbf{Unchanged} & \textbf{Not Met --} Dependent on predictive modelling feature, which was not implemented. \\

\bottomrule
\end{xltabular}

\subsubsection{Project Objectives}

These objectives represent the stakeholder requirements and provide a framework for evaluating how the implemented features support the operational needs of the SPIO department. 

\begin{enumerate}
    \item \textbf{Improve Data Freshness:} Generating updated competitor information allows the department to monitor changes throughout the year and reduces reliance on a third-party outdate dataset.
    \item \textbf{Control Data Coverage:} Data is collected from sources such as UCAS and specific institutional websites, allowing in-depth programme data to be collected for targeted universities. 
    \item \textbf{Improve Analytical Capability:} Tools such as searching, filtering and exporting enables users to quickly locate programmes for their research and prepare datasets for further analysis. 
    \item \textbf{Competitor Analysis:} Comparison of programmes and visualisation of course information to identify patterns and differences between institutions. 
\end{enumerate}
\begin{comment}
\paragraph{Objective 1 - Improve Data Freshness}
The capability to generate updated competitor information allows the department to monitor changes throughout the year and reduces reliance on a third-party outdate dataset.

\paragraph{Objective 2 - Control Data Coverage}
Data is collected from sources such as UCAS and specific institutional websites, allowing in-depth programme data to be collected for targeted universities. 

\paragraph{Objective 3 - Improve Analytical Capability}
Tools such as searching, filtering and exporting enables users to quickly locate programmes for their research and prepare datasets for further analysis. 

\paragraph{Objective 4 - Competitor Analysis}
Comparison of programmes and visualisation of course information to identify patterns and differences between institutions. 
\end{comment}
\subsubsection{Feature Mapping}
%This table maps the implemented behavioural features to the project objectives, demonstrating how the system functionality achieves the stakeholder goals and requirements. 
\vspace{-20pt}
\begin{table}[h]
\centering
\begin{xltabular}{\textwidth}{@{} l X l} 
\caption{Mapping behavioural features to project objectives and stakeholder requirements} \\
\toprule
\textbf{Feature} & \textbf{Description} & \textbf{Objectives} \\
\midrule
Login & Secure authentication allowing authorised staff system access & -- \\
Data Fetching & Collection of course data from UCAS and institution websites & O1, O2 \\
Exporting Data & Export filtered datasets to Excel for external analysis & O3 \\
Data Visualisation & Visualise course dataset information and trends & O4 \\
Searching Data & Keyword search for finding courses & O3 \\
Filtering Data & Filter course list based on institution and other course attributes & O3 \\
Dashboard Overview & Display key competitor comparison metrics & O4 \\
Course Comparison & Side-by-side comparison of multiple selected courses & O4 \\
\bottomrule
\end{xltabular}
\end{table}
\vspace{-16pt}