% ==========================================
% SECTION 3: USE INSTRUCTIONS (20%)
% ==========================================
\section{Use Instructions}

\subsection{Installation}
% System requirements (HW/SW), step-by-step install.

This section outlines the system requirements and installation process to run the application locally.

\subsubsection{System Requirements}

\begin{table}[h]
\centering
\begin{tabular}{@{} l l l @{}}
\toprule
\textbf{Component} & \textbf{Minimum Requirement} & \textbf{Recommended} \\
\midrule
CPU & Dual-core processor & Quad-core processor \\
RAM & 4 GB & 8+ GB \\
Storage & 10 GB free space & 20 GB free space \\
Operating System & Windows 10+, macOS 12+, Ubuntu 22.04+ & -- \\
\bottomrule
\end{tabular}
\caption{Hardware and operating system requirements}
\end{table}

These requirements define the resources needed to run the system locally. Recommended specifications improve performance when running additional tasks, such as web scraping, alongside the application. 

\subsubsection{Software Requirements}

To run the system locally, several software components must be installed to provide the runtime environment for the backend API, frontend application and database used by the system. 

\begin{table}[h]
\centering
\begin{tabularx}{\textwidth}{@{} l l X @{}}
\toprule
\textbf{Software} & \textbf{Version} &\textbf{Purpose} \\
\midrule

Node.js & v18 + & Provides runtime environment for backend application server, providing data collection, processing and API functionality. \\

npm & Included with Node.js & Install and manage backend and frontedn software packages. \\

PostgreSQL & v14 + & Relational database storing collected course and institution data. \\

Git & Latest stable release & Retrieve system source code from the project repository. \\

Web Browser & Latest version & Interact with system's web-based user interface locally. \\

\bottomrule
\end{tabularx}
\caption{Software dependency requirements}
\end{table}

The third-party software listed above must be installed before deploying the application. Installation instructions for these dependencies are available in their official documentation \cite{git, nodejs, postgresql}.
The system's web-based scraping functionality uses the Puppeteer library, which downloads a compatible headless Chromium browser to load and extract data from university webpages. 

\subsubsection{Installation Procedure}

\paragraph{1. Retrieve Source Code} The system source code can be obtained from the project repository. This command downloads the project files and navigates into the project directory.

\begin{commandbox}
git clone https://github.com/COMP2281/software-engineering-group25-26-19.git \\
cd \textless project\_directory\textgreater
\end{commandbox}

\paragraph{2. Install Backend Dependencies} The backend server dependencies must be installed to enable the backend application server and scraping capabilities. 

\begin{commandbox}[/backend]
npm install
\end{commandbox}

\paragraph{3. Install Frontend Dependencies} The frontend dependencies must be installed to run the React user interface utilising the required packages. 

\begin{commandbox}[/frontend]
npm install
\end{commandbox}

\paragraph{4. Configure Environment Variables} 
Backend functionality requires environment variables to access the database and admin account. Create a \texttt{.env} file in the backend directory containing these settings. The port will default to 5001 if not specified. The remaining values are set during database configuration and initial account setup, (Sections~\ref{sec:deployment} and~\ref{sec:launching}).

\begin{commandbox}
DATABASE\_URL=\textless postgresql\_database\_url\textgreater \\
ADMIN\_PASSWORD\_HASH=\textless hashed\_admin\_password\textgreater \\
PORT=\textless selected\_port\textgreater
\end{commandbox}


\subsection{Deployment}
\label{sec:deployment}
% Local machine deployment, database setup, VMs/Containers/Cloud.

Once installed, the application must be configured and deployed before users can interact with the system. 

\paragraph{1. Create PostgreSQL Database} The system requires a PostgreSQL database to store the data collected from UCAS and individual institution websites in a structured format. Database name must match the \texttt{DATABASE\_URL} environment variable.

\begin{commandbox}
createdb spio\_course\_db
\end{commandbox}

\paragraph{2. Generate Administrator Password Hash} An account is required to access the protected frontend routes. A script is provided to generate a secure bcrypt hash for the admin password. The output hash must be set as the \texttt{ADMIN\_PASSWORD\_HASH} envirnment variable. 

\begin{commandbox}
npx ts-node backend/src/scripts/createPassword.ts \textless password\textgreater
\end{commandbox}

\paragraph{3. Initialise Prisma Database Schema} 
Prisma manages database access and schema, creating the required tables and backend client. These commands generate the prisma client and apply database migrations. 

\begin{commandbox}[/backend]
npx prisma generate \\
npx prisma migrate deploy
\end{commandbox}

\paragraph{4. Start Application Services} \label{start_app_services} Once the database is created, start the backend and frontend services to provide the system interface and API.

\begin{commandbox}[/backend]
npm run build \\
npm run start
\end{commandbox}

\subsection{Launching}
\label{sec:launching}
% User account creation, login, different roles, first-time setup.

Once the application services have been started during deployment, the system can be accessed through a web browser. The following steps describe how to access and perform the initial setup required to use the platform. 

\paragraph{1. Access Web Application}

Once the application services are running, open the system in a browser to access the login page and protected routes. Routing to a sub-page will redirect to the login, then the requested protected route. 

\begin{commandbox}
http://localhost:PORT
\end{commandbox}

\paragraph{2. Authenticate with Administrator Account}
Log in using the administrator account created during deployment. Upon authentication, user is redirected to dashboard, or specific sub-page routed to in the URL. Authentication provides access to course data pages, scraping tools and export functionality, and is managed using a session-based token. 

\begin{commandbox}
Username: admin \\
Password: \textless admin\_password\textgreater
\end{commandbox}

\paragraph{3. Initial Data Scrape}
On launch, the database is empty, so competitor course data must be collected. From the dashboard, the user can initialise the collection process by clicking the \texttt{Quick Fetch} button, with the interface indicating 'in progress' or 'completed'.

\subsection{Troubleshooting}
% Common error messages, solutions, log locations.
This section outlines common issues that may occur, hindering system functionality or usability during installation, deployment or at runtime, in addition to recommended solutions and available diagnostic tools.

\subsubsection{Installation Issues}

The following table outlines common issues that can occur during installation, preventing system use, and the steps to resolve them. 

\begin{table}[h]
\centering
\begin{tabularx}{\textwidth}{@{} p{2.5cm} p{5cm} X @{}}
\toprule
\textbf{Issue} & \textbf{Cause} & \textbf{Resolution} \\
\midrule

\texttt{Git} not recognised & Git dependency not installed or not added to system PATH. & Install git using official documentation \cite{git}, verify using \texttt{git --version} in destination folder. \\

\texttt{node} not recognised & Node.js not installed or not added to system PATH. & Install Node.js, version 18 +, using official documentation \cite{nodejs}, and verify \texttt{node -v} in the project directory. \\

\texttt{npm install} failure & Missing, incompatible or interrupted Node.js installation. & Ensure Node.js installed, version 18 +, delete \texttt{node\_modules} folder and retry \texttt{npm install}. \\

Database connection error & PostgreSQL not initialised or incorrect connection string. & Ensure PostgreSQL installed using official documentation \cite{postgresql}, and running. Verify \texttt{DATABASE\_URL} in \texttt{.env} file. \\

Database does not exist & PostgreSQL database not created before deployment. & Create database using command \texttt{createdb spio\_course\_db}. \\

Prisma migration fails & Database connection is invalid or migrations not generated. & Verify database connection and run \texttt{npx prisma migrate reset}. \\

\bottomrule
\end{tabularx}
\caption{Common installation issues and recommended fixes}
\end{table}
\vspace{-20pt}

\subsubsection{Application Issues}
The following section outlines issues that can occur during normal usage of the system through the web interface. 

\begin{table}[h]
\centering
\begin{tabularx}{\textwidth}{@{} p{2.5cm} p{5cm} X @{}}
\toprule
\textbf{Issue} & \textbf{Cause} & \textbf{Resolution} \\
\midrule

App not available in browser & Backend server not running or incorrect port used. & Ensure the backend server is running (Section \ref{start_app_services}), and verify the correct port is used in browser. \\

Login failure & Incorrect admin password or password hash not configured. & Regenerate password hash using provided script and update \texttt{ADMIN\_PASSWORD\_HASH} in the \texttt{.env} file. \\

No course data visible & Database not populated with scraped data. & Navigate to dashboard page and run \texttt{Quick Fetch}. Data will be populated as process executes. \\

\bottomrule
\end{tabularx}
\caption{Common application issues and recommended fixes}
\end{table}
\vspace{-20pt}

\subsubsection{Logs and Diagnostics}

Diagnostic information can be found in the terminal used to initialise the backend server, with runtime errors and database issues are displayed in the console output. Scraping diagnostics are written to the \texttt{logs} directory for further inspection if required. Any frontend errors will appear on the respective pages and also in the browser development tools (F12), where JavaScript errors and network requests can be investigated. 